---
title: "Using connector without YAML files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using connector without YAML files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(connector)
library(dplyr)
```

```{r, include = FALSE}
# Use a temporary directory for examples
tmp_dir <- withr::local_tempdir()
knitr::opts_knit$set(root.dir = tmp_dir)
```

```{r}
# Create directories for examples
dir.create("data", showWarnings = FALSE)
dir.create("raw", showWarnings = FALSE)
dir.create("processed", showWarnings = FALSE)
dir.create("output", showWarnings = FALSE)
```


This vignette shows how to create and use connector objects directly in R code without YAML configuration files.

## Creating Individual Connectors

You can create connector objects directly using the specific connector functions:

### File System Connector

```{r}
# Create a file system connector
fs_conn <- connector_fs(path = "data")
fs_conn
```

### Database Connector

```{r}
# Create a database connector (using SQLite)
if (requireNamespace("RSQLite", quietly = TRUE)) {
  db_conn <- connector_dbi(
    drv = RSQLite::SQLite(),
    dbname = ":memory:"
  )
  db_conn
}
```

## Using Individual Connectors

```{r}
# Write and read data
sample_data <- mtcars[1:5, 1:3]

fs_conn |> write_cnt(sample_data, "cars.csv")
fs_conn |> list_content_cnt()

retrieved_data <- fs_conn |> read_cnt("cars.csv")
head(retrieved_data)
```

## Creating Multiple Connectors with `connectors()`

The `connectors()` function lets you group multiple connector objects together:

```{r}
# Create a collection of connectors
my_connectors <- connectors(
  raw = connector_fs(path = "raw"),
  processed = connector_fs(path = "processed")
)

my_connectors
```

## Working with Multiple Connectors

```{r}
# Use different connectors for different purposes
iris_sample <- iris[1:10, ]

# Store raw data
my_connectors$raw |> write_cnt(iris_sample, "iris_raw.rds")

# Process data
processed <- iris_sample |>
  group_by(Species) |>
  summarise(mean_length = mean(Sepal.Length))

# Store processed data
my_connectors$processed |> write_cnt(processed, "iris_summary.csv")

# Check contents of each connector
my_connectors$raw |> list_content_cnt()
my_connectors$processed |> list_content_cnt()
```

## Mixed Storage Types

You can combine different types of connectors:

```{r}
if (requireNamespace("RSQLite", quietly = TRUE)) {
  # Mix file system and database connectors
  mixed_connectors <- connectors(
    files = connector_fs(path = "output"),
    database = connector_dbi(RSQLite::SQLite(), dbname = ":memory:")
  )

  # Same data, different storage
  test_data <- data.frame(x = 1:3, y = letters[1:3])

  mixed_connectors$files |> write_cnt(test_data, "test.csv")
  mixed_connectors$database |> write_cnt(test_data, "test_table")

  # List contents
  mixed_connectors$files |> list_content_cnt()
  mixed_connectors$database |> list_content_cnt()
}
```

## Nested Connectors with `nested_connectors()`

You can group multiple `connectors()` objects together using `nested_connectors()`:

```{r}
# Create connectors for different projects
project_a <- connectors(
  raw = connector_fs(path = "raw"),
  processed = connector_fs(path = "processed")
)

project_b <- connectors(
  data = connector_fs(path = "data"),
  output = connector_fs(path = "output")
)

# Group them in a nested structure
all_projects <- nested_connectors(
  project_a = project_a,
  project_b = project_b
)

all_projects
```

Now you can access connectors through the nested structure:

```{r}
# Access connectors through nested structure
sample_data <- data.frame(x = 1:3, y = letters[1:3])

# Project A operations
all_projects$project_a$raw |> write_cnt(sample_data, "sample.rds")
all_projects$project_a$raw |> list_content_cnt()

# Project B operations
all_projects$project_b$data |> write_cnt(sample_data, "input.csv")
all_projects$project_b$data |> list_content_cnt()
```

## Benefits of Using `connectors()`

- **Organization**: Group related storage locations together
- **Flexibility**: Mix different storage types (files, databases)
- **Consistency**: Same interface for all storage types
- **Clarity**: Named connectors make code more readable

## Summary

- Use `connector_fs()` and `connector_dbi()` to create individual connectors
- Use `connectors()` to group multiple connectors together
- Access individual connectors by name: `my_connectors$name`
- All connectors use the same functions: `write_cnt()`, `read_cnt()`, `list_content_cnt()`, `remove_cnt()`